Analysis for Performing-Articulation performances (DURATION)

### 2020-05-13 material/analysis/expression/stim_a/ioi_duration.Rmd
edit outlines
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Sequence plot
#### All
```{r duration_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[Subcomponent != "NA", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

>>>>

### Sequence plot
- Right wrap: Subject Number

#### All
```{r duration_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[Subcomponent != "NA", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]
